---
title: "Epi 590R Final Project"
author: "Parth Jariwala"
format: html
editor: visual
execute: 
  echo: false
  warning: false
---

The following document displays descriptive statistics, a figure, and regression analysis of an older data set collected by the author for a previous course, EH 510. Data collection was done by collecting ambient air and different particulate matter (PM1, PM2.5, and PM10) and volatile organic compound (VOCs) concentrations while visiting different bus stops in the North Druid Hills area. PM2.5 concentrations will be the main variable of focus in this analysis.

```{r}
#| output: false

library(tidyverse)
library(gtsummary)

day1_cols <- c("time", "voc_ppm", "aqs", "temperature_c", "humidity_percent", "pressure_mbar", "pm1_ug_m3", "pm2_5_ug_m3", "pm10_ug_m3", "latitude","longitude", "bus_stop")

day1 <- read_csv(here::here("data", "raw", "Day1_Copy.csv"),
								 skip =1, col_names = day1_cols) %>% 
		janitor::clean_names() %>% 
mutate(stop_cat = factor(bus_stop,
		levels = c(1, 2, 3, 4),
    labels = c("Book Nook Stop", 
    "Clairmont Stop", 
    "Kroger Stop", 
    "Steak 'N Shake Stop")))
```

```{r}
#| label: tbl-one
#| echo: false
#| tbl-cap: Descriptive Statistics by Bus Stop
table1 <- tbl_summary(
	day1,
	by = stop_cat,
	include = c(voc_ppm, pm1_ug_m3, 
							pm2_5_ug_m3, pm10_ug_m3), 
			label = list(
      voc_ppm ~ "VOC (ppm)",
      pm1_ug_m3 ~ "PM1 (µg/m³)",
      pm2_5_ug_m3 ~ "PM2.5 (µg/m³)",
      pm10_ug_m3 ~ "PM10 (µg/m³)"
    ),
	missing_text = "Missing"
  ) %>%
  add_overall(last = TRUE) %>%
  modify_header(label ~ "**Variable**") %>%
  bold_labels()

table1
```

@tbl-one displays the particulate matter and VOC concentrations at different bus stops. The median and IQR are `r inline_text(table1, variable = "pm2_5_ug_m3", column = "stat_0")`.

```{r}
stats <- list(n = nrow(day1), mean_pm2_5 = mean(day1$pm2_5_ug_m3, na.rm = TRUE))
```

The experiment on Day 1 took `r stats$n` minutes and the average PM 2.5 concentration was `r stats$mean_pm2_5` µg/m3

```{r}
#| echo: false
hist1 <- ggplot(day1) +
	aes(x = pm2_5_ug_m3) +
	geom_histogram()
```

```{r}
#| echo: false
#| output: false
ggsave(plot = hist1,
			 filename = here::here("data", "figures", "hist1.pdf"))
```

```{r}
#| label: fig-hist
#| fig-cap: Frequency of PM2.5 Concentrations on Day 1
#| echo: false
hist1
```

@fig-hist displays a histogram of PM2.5 concentrations over a one hour sampling period on Day 1

```{r}
#| label: tbl-two
#| tbl-cap: Linear Regression Model Summary for PM2.5 Concentration
#| echo: false

linear_model <- lm(pm2_5_ug_m3 ~ temperature_c + stop_cat, data = day1)


table2_function <- function(model) {
	tbl_regression(
	linear_model,
	intercept = FALSE,
	label = list(
		temperature_c ~ "Temperature (C)",
		stop_cat ~ "Bus Stop"
	)) %>% 
	 modify_header(label ~ "**Variable**") %>% 
	bold_labels()
}

table2_function(linear_model)
```

@tbl-two displays the relationship between PM2.5, temperature (C), and bus stop location in a linear regression table.
